%-------------------------
% Resume in Latex
% Author : Spiros Vathis
% License : MIT
%------------------------

\documentclass[letterpaper,10pt]{article}

\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage[usenames,dvipsnames]{color}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{verbatim}

% Define global list margin
\newlength{\listmargin}
\setlength{\listmargin}{15pt}

\pagestyle{fancy}
\fancyhf{} % clear header/footer
\cfoot{\thepage} % center footer with page number
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-4pt}]

\pdfgentounicode=1

% Simple commands for consistent lists
\newcommand{\resumeItem}[1]{
  \item\small{#1}
}
\newcommand{\resumeHeading}[4]{
    \textbf{#1} \hfill #2\\
    \textit{\small #3} \hfill \textit{\small #4}\\[4pt]
}
\newcommand{\resumeSubheading}[4]{
  \vspace{2pt}\noindent\textbf{#1} --- #2 \hfill #3\\
  \textit{\small #4}\vspace{4pt}
}
\setlength{\footskip}{15pt}
\begin{document}

% Header: plain text for ATS
\begin{center}
  {\LARGE \textbf{Spiros Vathis}}\\[6pt]
  spiros.vathis@gmail.com \; | \; +30 694 4332973 \; | \; github.com/sVathis \; | \; linkedin.com/in/vathis
\end{center}

\section{Professional Summary}
Experienced software engineer with more than 25 years of experience designing and implementing high-performance, data-intensive, real-time systems. Strong background in platform engineering, system \& network programming, distributed systems, cloud-native architectures, performance optimization, and team leadership. Proven track record across enterprise, cloud, and startup environments. Mathematical background that provides analytical thinking skills required in acute problem solving situations. Holds a B.Sc. in Mathematics and an M.Sc. in Information Systems.

% \section{Technical Skills}
% \begin{itemize}[leftmargin=\listmargin,noitemsep]
%   \item Languages: Python, C++, SQL, JavaScript, C
%   \item Cloud \& Platforms: Azure, AWS, Kubernetes (EKS), Docker, ACI
%   \item Data \& Observability: ETL, Telemetry pipelines, CI/CD, SQL-as-Code change management
%   \item Tools \& OS: Linux, FreeBSD, Solaris, OpenGL, OpenCV, Matplotlib
%   \item Practices: Performance tuning, reliability engineering, containerization, schema lifecycle management
% \end{itemize}

\section{Professional Experience}
\noindent\textbf{Staff Software Engineer} --- Netscaler / Cloud Software Group \hfill Patras, Greece \hfill Oct 2023 -- Dec 2025
\begin{itemize}[leftmargin=\listmargin,noitemsep]

  \resumeItem{\textbf{Governance \& CI/CD Maturity:}}
     {Established full containerization for ETL telemetry data workloads in Python and introduced SQL-as-code for schema lifecycle management, improving deployment consistency, traceability and integration with CI/CD workflows.}
  \resumeItem{\textbf{Observability \& Data Quality:}}
    {Delivered telemetry pipelines, visualization dashboard (PowerBI) integration, active-usage aggregation. Also delivered a Telemetry Validation Playbook, strengthening system observability and proactive detection of data inconsistencies.}
  \resumeItem{\textbf{Cross-team Enablement:}}
    {Produced comprehensive ETL pipeline documentation, archived legacy data to improve database performance and authored a telemetry extension guide adopted by feature teams to accelerate onboarding and reduce implementation effort.}
  \resumeItem{\textbf{Reliability Engineering:}}
    {Eliminated Netscaler management CPU spikes during telemetry colleciton, through redesigned counter-retrieval logic and replaced long-running ETL daemons with scheduled, immutable container executions, significantly improving platform reliability and operational efficiency.}
\end{itemize}

\noindent\textbf{Principal Software Engineer} --- mismatch.ai \hfill Patras, Greece \hfill Mar 2022 -- Jul 2023
\begin{itemize}[leftmargin=\listmargin,noitemsep]
  \resumeItem{\textbf{Stream Orchestration:}}
    {Led design and Python development of a live-streaming orchestrator service on AWS with a REST API to manage basketball real-time video game streams.}

  \resumeItem{\textbf{Cloud Deployment:}}
    {Implemented containerized Python services deployed to Kubernetes (EKS); managed images in Amazon ECR and deployments via Kubernetes API.}

  \resumeItem{\textbf{C++ Visualization:}}
    {C++ developement of streamer K8S pod for visualization of game statistics using OpenCV and Matplotlib; containerized and orchestrated on EKS by orchastrator above.}

\end{itemize}

\noindent\textbf{Principal / Staff Software Engineer} --- Citrix Inc. \hfill Patras, Greece \hfill Jul 2012 -- Nov 2021
\begin{itemize}[leftmargin=\listmargin,noitemsep]
  \resumeItem{\textbf{Team Leadership:}}
    {Led teams (4--10 engineers) delivering Citrix SD-WAN Edge Security (IDS, web filtering, anti-malware) and Citrix ADC Hybrid Multicloud features.}

  \resumeItem{\textbf{Azure Integration:}}
    {Designed and implemented Azure integrations using Azure SDK for Python and multiple Azure REST APIs; integrated cloud features into existing product frameworks.}

  \resumeItem{\textbf{Performance Scaling:}}
    {Led performance refactoring for a legacy CDN analytics platform, increasing ingestion from 90K rec/s to 500K rec/s and end-to-end throughput from 125K rec/s to 1.25M rec/s.}

  \resumeItem{\textbf{REST API \& Service:}}
    {Designed S3-like REST API and scalable server platform for content acceleration; influenced adoption of modern scalable tech (Node.js, Couchbase).}

  \resumeItem{\textbf{Systems Programming:}}
    {Implemented performance-critical components in C on FreeBSD and supported product field teams for demos and issue triage for telco customers.}

\end{itemize}

\noindent\textbf{Senior Software Engineer} --- Bytemobile Inc. \hfill Patras, Greece \hfill Apr 2008 -- Jul 2012
\begin{itemize}[leftmargin=\listmargin,noitemsep]
  \resumeItem{Head developer for Flash Adaptation framework in the Unison platform and implemented server-side HTML content adaptation using Mozilla Gecko rendering engine.}
  \resumeItem{Maintained the 'C' legacy codebase of a high-performance Content Adaptation HTTP proxy.}
\end{itemize}

\noindent\textbf{Senior Software Engineer} --- Pi-Medical Ltd. \hfill Athens, Greece \hfill Dec 2001 -- Mar 2008
\begin{itemize}[leftmargin=\listmargin,noitemsep]
  \resumeItem{Designed and implemented a 3D simulation application for linear accelerators (collision detection) using C++ and OpenGL on Windows; produced documentation required for 'CE' certification.}
\end{itemize}

\noindent\textbf{Software Engineer} --- Expertnet S.A. \hfill Patras, Greece \hfill Apr 1997 -- May 2000
\begin{itemize}[leftmargin=\listmargin,noitemsep]
  \resumeItem{Developed a S/MIME - PEM cryptography plugin for Eudora mail client using Visual C++ for Windows.}
\end{itemize}

\section{Academic Experience}
\noindent\textbf{Assistant Laboratory Professor} --- TEI of Patra, Dept. of Mass Media \& Informatics \hfill Pyrgos, Greece \hfill Sept 2006 -- Jun 2008
\begin{itemize}[leftmargin=\listmargin,noitemsep]
  \resumeItem{Freshman course tutor in Introduction to Computer Programming (Pascal).}
\end{itemize}

\noindent\textbf{Instructor} --- Greek Mathematics Society \hfill Patras, Greece \hfill 1999 -- 2000
\begin{itemize}[leftmargin=\listmargin,noitemsep]
  \resumeItem{Delivered vocational training on DOS, Windows, and C programming.}
\end{itemize}

\section{Education}
\noindent\textbf{Master of Science in Information Systems}\\Open University of Cyprus \hfill Nicosia \hfill 2008 -- 2011\\
\noindent\textbf{Bachelor in Mathematics}\\University of Patras \hfill Patras, Greece \hfill 1991 -- 1996

\section{Patent}
\noindent\textbf{US9075877} \\ System and method for transparent in-network adaptation of rich internet applications \hfill Issued Jun 29, 2012\\
Inventors: Tsolis G., Zafiris P., Vathis S.

\section{Pet project}
\noindent\textbf{Self hosted home lab} \\
Designed and implemented a self-hosted home lab using Docker for containerization, Cloudflare Zero Trust reverse proxy \& Wireguard for secure remote acces, and various open-source tools for network monitoring and management.\\
Self hosted services include:
\begin{itemize}[leftmargin=\listmargin,noitemsep]
    \resumeItem{\textbf{Immich}}{for personal photo management}
    \resumeItem{\textbf{Home Assistant}}{for smart home automation}
    \resumeItem{\textbf{AdGuard Home}}{for network-wide ad blocking and privacy protection}
    \resumeItem{\textbf{Dawarich}}{for self hosted location history}
    \resumeItem{\textbf{Paperless-ngx}}{for document management}
    \resumeItem{\textbf{Cloudflare Zero Trust} reverse proxy and self hosted \textbf{Wireguard}}service {for secure remote access}
    \resumeItem{\textbf{Navidrome}}{for personal music streaming
    }
    \resumeItem{Several other custom build containers in Python that server special needs}
\end{itemize}
\end{document}